%\documentclass{...}
\input{./def/yf-formatting}

\usepackage{amsfonts, amsmath, amssymb, amsthm}
\usepackage{comment} 
\usepackage{graphicx}
\usepackage{ifthen}
\usepackage{latexsym}
%\usepackage{times}

\input{./def/yf-def}
\def\A{\mathcal{A}}
\def\C{\EuScript{C}}
\def\S{\EuScript{S}}
\def\dist{\mathit{dist}}

\def\A{\mathcal{A}}

\newboolean{solver}\setboolean{solver}{false}
%\newboolean{solver}\setboolean{solver}{true}
\ifthenelse{\boolean{solver}}{\includecomment{sol}}{\excludecomment{sol}}

\def\extraspacing{\vspace{5mm} \noindent}


\begin{document}

\extraspacing {\bf Problem 1.} Consider the merging problem in our PRAM discussion. Let $A_1$ be the array $(1, 17, 28, 29, 55, 61, 69, 80)$ and $A_2$ be the array $(10, 13, 25, 33, 38, 56, 72, 75)$. Give the content of array $B_1$.


\begin{sol} 
    \extraspacing {\bf Solution.} $B_1 = (1, 4, 6, 7, 10, 12, 13, 16)$.
\end{sol}

\extraspacing {\bf Problem 2.} Consider the sorting problem in EM. Let $A$ be the input file of $n$ integers (which is stored in $O(n/B)$ blocks). Give an algorithm to produce $O(n/M)$ files satisfying all the following requirements: 
\myitems{
    \item Each file stores at most $M$ integers of $A$ in ascending order using $O(M/B)$ blocks. 
    \item All the files are mutually disjoint. 
    \item The union of all the files is the set of integers in $A$.
}
Your algorithm must terminate in $O(n/B)$ I/Os. 

\begin{sol}
    \extraspacing {\bf Solution.} Load the first $M$ numbers of $A$ into memory, sort them, and then write the sorted list into a file of $O(M/B)$ blocks. Then, do the same to the next $M$ numbers of $A$. Repeat until having exhausted $A$. 
\end{sol}

\extraspacing {\bf Problem 3.} This question concerns the PRAM model. Suppose that we have already obtained a sorting algorithm $\A$ finishing in $f(n)$ steps when the number $p$ of CPUs equals $n$ (recall that $n$ is the number of integers to sort). Consider now the scenario where $p < n$. Describe how to use $\A$ to design an algorithm that finishes in $O(\fr{n}{p} \cdot f(n))$ steps.

\begin{sol}
    \extraspacing {\bf Solution.} The key is to simulate a step of $\A$, which runs on $n$ CPUs, by performing $O(n/p)$ steps with $p$ CPUs. I suggest giving a full mark as long as the student manages to make the above observation.

    \vgap

    For a complete answer, however, we must clarify the details of the reduction. Let $\Upsilon_1, \Upsilon_2, ..., \Upsilon_n$ be the $n$ CPUs of $\A$; call them the {\em $\A$-CPUs}. Define the {\em state} of each $\Upsilon_i$ ($i \in [1, n]$) as the current set of register values in $\Upsilon_i$. To simulate $\A$, we preserve the state of every $\Upsilon_i$ in $O(1)$ special memory words.

    \vgap

    We simulate every step of $\A$ --- call this an {\em $\A$-step} --- in $O(n/p)$ steps through $\lc n / p \rc$ phases. The $i$-th ($i \in [1, n]$) phase executes the atomic operations performed by $\Upsilon_{i \cdot p+1}, \Upsilon_{i \cdot p+2}, ..., \Upsilon_{(i+1) \cdot p}$ during the $\A$-step. For this purpose, we first perform $O(1)$ steps to load the state of $\Upsilon_j$, for each $j \in [i \cdot p+1, (i+1) \cdot p]$, into the $(j \mod p)$-th CPU. The atomic operations of the $p$ CPUs can then be carried out in another step. Because $\A$ is a CREW algorithm, no two CPUs can have a conflict in memory accesses during an $\A$-step. Therefore, we guarantee that the states of all $\A$-CPUs after   the $\lc n / p \rc$ phases are identical to those after the $\A$-step.
\end{sol}

\extraspacing {\bf Problem 4.} Give a PRAM algorithm that settles the sorting problem in $O(\fr{n}{p} \log^2 n)$ steps.

\begin{sol}
    \extraspacing {\bf Solution.} Apply the reduction in Problem 3 to our discussion in the seminar.
\end{sol}


\end{document}
