%\documentclass{...}

\input{./def/yf-formatting}

\usepackage{amsfonts, amsmath, amssymb, amsthm}
\usepackage{comment} 
\usepackage{graphicx}
\usepackage{ifthen}
\usepackage{latexsym}
%\usepackage{times}

\input{./def/yf-def}

\newboolean{solver}\setboolean{solver}{false}
%\newboolean{solver}\setboolean{solver}{true}
\ifthenelse{\boolean{solver}}{\includecomment{sol}}{\excludecomment{sol}}


\begin{document}

\section*{Exercises}

\extraspacing {\bf Problem 1.} Which of the following can be a property of a minimal sorting algorithm? 


\vgap

\noindent A.\ It performs $O(\log n)$ supersteps, where $n$ is the number of elements to sort. \\
\noindent B.\ It requires a machine to send $O(n/p^{0.99})$ words in some superstep. \\
\noindent C.\ It requires a machine to spend $O((n/p) \log (n/p))$ CPU time in some superstep. \\
\noindent D.\ It requires a machine to use $O(n/p^{0.99})$ space in some superstep. 

\begin{sol}
   \extraspacing {\bf Solution.} C.
\end{sol}


\extraspacing {\bf Problem 2.} In the seminar, we introduced a minimal algorithm for sorting. Assuming that each machine has $n/p$ elements in its local storage at the beginning of the algorithm, answer the following questions: 
\myitems{
    \item [(a)] In Phase 1, how many elements are sampled from each machine in expectation? 
    \item [(b)] Still in Phase 1, how many elements does each machine {\em receive} in expectation?
}

\begin{sol}
   \extraspacing {\bf Solution.} (a) Since each element is sampled with probability $(p/n) \ln(np)$, the expected number of elements sampled is $(n/p) \cdot (p/n) \ln(np) = \ln(np)$. 
   
   \vgap 
   
   (b) Each machine receives the sample elements from all other machines. Therefore, it receives $(p-1) \ln(np)$ elements in expectation. 
\end{sol}

\extraspacing {\bf Problem 3.} In our argument for proving the lower bound on the load of the cartesian product problem, we had the sentence: ``Machine 1 sees $n + L$ elements overall $\Rightarrow$ it can produce at most $(\fr{n+L}{2})^2$ pairs.'' Give a proof of the sentence.

\begin{sol}
   \extraspacing {\bf Solution.} Let $x$ and $y$ be the number of red and blue elements Machine 1 sees, respectively. Thus, $x + y \le n + L$. The number of pairs that can be produced by Machine 1 is $xy$. We have: 
   \myeqn{
        \sqrt{xy} &\le& (x+y)/2 \hspace{10mm} \Rightarrow \nn \\
        xy &\le& ((x+y)/2)^2 \hspace{10mm} \Rightarrow \nn \\ 
        &=& \left(\fr{n+L}{2}\right)^2. \hspace{10mm} \nn 
   }
\end{sol}
\end{document}
